Resurgence of the Airy function \\ and other exponential integrals

### 2022-08-19 exp-resurgence.tex
Fix K_{1/3} integral computation using Sage
See `expansion.sage`.
Fix sign error in Bessel integral example
Drop Bessel integral example scratch work

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}
\subsubsection{Setting}
You can often find a formal power series
\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
\color{SeaGreen}
\begin{align*}
\zeta_\alpha & = -1 \\
\tfrac{1}{2} \tau^2 & = f - \zeta_\alpha \\
& = 4u^3 - 3u + 1 \\
\tau & = 0 \text{ and } u_\tau = 0 \text{ at } u = \tfrac{1}{2} \\
\tfrac{1}{2} \tau^2 & = 6w^2 + 4w^3 \text{ with } u := \tfrac{1}{2} + w \\
I_\alpha(z) & = e^{z\zeta_\alpha} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \\
& = e^{-z} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu
\end{align*}
\begin{align*}
w & = \sum_{n = 1}^\infty a_n \tau^n \\
w^2 & = \sum_{n = 2}^\infty \left( \sum_{k + k' = n} a_k a_{k'} \right) \tau^n \\
& = a_1^2 \tau^2 + 2 a_1 a_2 \tau^3 + (2 a_1 a_3 + a_2^2) \tau^4 + (2 a_1 a_4 + 2 a_2 a_3) \tau^5 + (2 a_1 a_5 + 2 a_2 a_4 + a_3^2) \tau^6 + \ldots \\
w^3 & = \sum_{n = 3}^\infty \left( \sum_{k + k' + k'' = n} a_k a_{k'} a_{k''} \right) \tau^n \\
& = a_1^3 \tau^3 + 3 a_1^2 a_2 \tau^4 + (3a_1 a_2^2 + 3 a_1^2 a_3) \tau^5 + (3 a_1^2 a_4 + 6 a_1 a_2 a_3 + a_2^3) \tau^6 + \ldots
\end{align*}
\begin{align*}
\tau^2 & = 12w^2 + 8w^3\\
\tau^2 & = 12 a_1^2 \tau^2 & 1 & = 12 a_1^2 \\
0 & = 24 a_1 a_2 \tau^3 + 8a_1^3 \tau^3 & 0 & = 36 a_2 + 12 a_1^2 \\
& & -1 & = 36 a_2 \\
0 & = (24a_1 a_3 + 12 a_2^2) \tau^4 + 24 a_1^2 a_2 \tau^4 & 0 & = 24 a_1 a_3 + 12 a_2^2 + 24 a_1^2 a_2 \\
& & & = 24 a_1 a_3 + 12 a_2^2 + 2 a_2 \\
& & & = 24 a_1 a_3 + \frac{1}{3 \cdot 36} - \frac{1}{18} \\
& & \frac{5}{108} & = 24 a_1 a_3 \\
& & \frac{5}{216} a_1 & = a_3 \\
0 & = (24 a_1 a_4 + 24 a_2 a_3) \tau^5 + (24 a_1 a_2^2 + 24 a_1^2 a_3) \tau^5 & 0 & = 24 a_1 a_4 + 24 a_2 a_3 + 24 a_1 a_2^2 + 2 a_3 \\
& & & = 24 a_1 a_4 + \frac{5}{9} a_2 a_1 + 24 a_1 a_2^2 + \frac{5}{108} a_1 \\
& & 0 & = 24 a_4 + \frac{5}{9} a_2 + 24 a_2^2 + \frac{5}{108} \\
& & 0 & = 24 a_4 - \frac{5}{324} + \frac{1}{54} + \frac{5}{108} \\
& & -\frac{4}{81} & = 24 a_4 \\
& & -\frac{1}{486} & = a_4 \\
\end{align*}
\begin{align*}
a_1 & = \frac{1}{\sqrt{12}} \\
2 a_2 & = -\frac{1}{18} \\
3 a_3 & = \frac{5}{72\sqrt{12}} \\
4 a_4 & = -\frac{2}{243} \\
du & = dw = w_\tau\,d\tau \\
& = \left[ \frac{1}{\sqrt{12}} - \frac{1}{18} \tau + \frac{5}{72\sqrt{12}} \tau^2 - \frac{2}{243} \tau^3 + \ldots \right] d\tau \\
& = \left[ 1 - \frac{1}{3\sqrt{12}} \tau + \frac{5}{72} \tau^2 - \frac{8}{81\sqrt{12}} \tau^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
& = \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
\end{align*}
\color{black}

@@

\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]

>>>>

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}
\subsubsection{Setting}
You can often find a formal power series
\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral

@@

% see expansion.sage
\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \frac{385}{216} \left(\frac{\tau}{\sqrt{12}}\right)^4 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
